---
format: gfm
info:
  v1_url: openproblems/tasks/dimensionality_reduction/README.md
  v1_commit: 817ea64a526c7251f74c9a7a6dba98e8602b94a8
toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(rlang)

strip_margin <- function(text, symbol = "\\|") {
  str_replace_all(text, paste0("(\n?)[ \t]*", symbol), "\\1") 
}

dir <- "src/dimensionality_reduction"
dir <- "."
```

# Label Projection

```{r description, echo=FALSE}
lines <- readr::read_lines(paste0(dir, "/docs/task_description.md"))
lines2 <- gsub("^#", "##", lines)
knitr::asis_output(lines2)
```

## Methods

Methods for assigning labels from a reference dataset to a new dataset.

```{r methods, echo=FALSE,warning=FALSE,error=FALSE,output="asis"}
method_ns_list <- processx::run("viash", c("ns", "list", "-q", "methods", "--src", "."), wd = dir)
method_configs <- yaml::yaml.load(method_ns_list$stdout)

method_info <- map_df(method_configs, function(config) {
  if (length(config$functionality$status) > 0 && config$functionality$status == "disabled") return(NULL)
  info <- as_tibble(config$functionality$info)
  info$comp_yaml <- config$info$config
  info$name <- config$functionality$name
  info$namespace <- config$functionality$namespace
  info$description <- config$functionality$description
  info
})
method_info$paper_doi <- method_info$paper_doi %||% NA_character_
method_info$code_url <- method_info$code_url %||% NA_character_

method_info_view <- 
  method_info %>%
    arrange(type, label) %>%
    transmute(
      Name = paste0("[", label, "](", comp_yaml, ")"),
      Type = type,
      Description = description,
      DOI = ifelse(!is.na(paper_doi), paste0("[link](https://doi.org/", paper_doi, ")"), ""),
      URL = ifelse(!is.na(code_url), paste0("[link](", code_url, ")"), "")
    )

cat(paste(knitr::kable(method_info_view, format = 'pipe'), collapse = "\n"))
```


## Metrics

Metrics for label projection aim to characterize how well each classifier correctly assigns cell type labels to cells in the test set.

```{r metrics, echo=FALSE,warning=FALSE,error=FALSE,output="asis"}
metric_ns_list <- processx::run("viash", c("ns", "list", "-q", "metrics", "--src", "."), wd = dir)
metric_configs <- yaml::yaml.load(metric_ns_list$stdout)

metric_info <- map_df(metric_configs, function(config) {
  metric_info <- as_tibble(map_df(config$functionality$info$metrics, as.data.frame))
  metric_info$comp_yaml <- config$info$config
  metric_info$comp_name <- config$functionality$name
  metric_info$comp_namespace <- config$functionality$namespace
  metric_info
})

metric_info$description <- metric_info$description %||% NA_character_
metric_info$label <- metric_info$label %||% NA_character_
metric_info$maximize <- metric_info$maximize %||% NA_character_
metric_info$min <- metric_info$min %||% NA_character_
metric_info$max <- metric_info$max %||% NA_character_

metric_info_view <- 
  metric_info %>%
    transmute(
      Name = paste0("[", label, "](", comp_yaml, ")"),
      Description = paste0(description, " ", ifelse(maximize, "Higher is better.", "Lower is better.")),
      Range = paste0("[", min, ", ", max, "]")
    )

cat(paste(knitr::kable(metric_info_view, format = 'pipe'), collapse = "\n"))
```


## Pipeline topology

```{r data, include=FALSE}
comp_yamls <- list.files(paste0(dir, "/api"), pattern = "comp_", full.names = TRUE)
file_yamls <- list.files(paste0(dir, "/api"), pattern = "anndata_", full.names = TRUE)

comp_file <- map_df(comp_yamls, function(yaml_file) {
  conf <- yaml::read_yaml(yaml_file)

  map_df(conf$functionality$arguments, function(arg) {
    tibble(
      comp_name = basename(yaml_file) %>% gsub("\\.yaml", "", .),
      arg_name = str_replace_all(arg$name, "^-*", ""),
      direction = arg$direction %||% "input",
      file_name = basename(arg$`__inherits__`) %>% gsub("\\.yaml", "", .)
    )
  })
})

comp_info <- map_df(comp_yamls, function(yaml_file) {
  conf <- yaml::read_yaml(yaml_file)

  tibble(
    name = basename(yaml_file) %>% gsub("\\.yaml", "", .),
    label = name %>% gsub("comp_", "", .) %>% gsub("_", " ", .)
  )
})

file_info <- map_df(file_yamls, function(yaml_file) {
  arg <- yaml::read_yaml(yaml_file)
  
  tibble(
    name = basename(yaml_file) %>% gsub("\\.yaml", "", .),
    description = arg$description,
    short_description = arg$info$short_description,
    example = arg$example,
    label = name %>% gsub("anndata_", "", .) %>% gsub("_", " ", .)
  )
})

file_slot <- map_df(file_yamls, function(yaml_file) {
  arg <- yaml::read_yaml(yaml_file)

  map2_df(names(arg$info$slots), arg$info$slots, function(group_name, slot) {
    df <- map_df(slot, as.data.frame)
    df$struct <- group_name
    df$file_name = basename(yaml_file) %>% gsub("\\.yaml", "", .)
    as_tibble(df)
  })
}) %>% 
  mutate(multiple = multiple %|% FALSE)
```

```{r flow, echo=FALSE,warning=FALSE,error=FALSE}
nodes <- bind_rows(
  file_info %>%
    transmute(id = name, label = str_to_title(label), is_comp = FALSE),
  comp_info %>%
    transmute(id = name, label = str_to_title(label), is_comp = TRUE)
) %>%
  mutate(str = paste0(
    "  ",
    id, 
    ifelse(is_comp, "[/", "("), 
    label,
    ifelse(is_comp, "/]", ")")
  ))
edges <- bind_rows(
  comp_file %>%
    filter(direction == "input") %>%
    transmute(
      from = file_name,
      to = comp_name,
      arrow = "---"
    ),
  comp_file %>%
    filter(direction == "output") %>%
    transmute(
      from = comp_name, 
      to = file_name, 
      arrow = "-->"
    )
) %>%
  mutate(str = paste0("  ", from, arrow, to))

# note: use ```{mermaid} instead of ```mermaid when rendering to html
out_str <- strip_margin(glue::glue("
  §```mermaid
  §%%| column: screen-inset-shaded
  §flowchart LR
  §{paste(nodes$str, collapse = '\n')}
  §{paste(edges$str, collapse = '\n')}
  §```
  §"), symbol = "§")
knitr::asis_output(out_str)
```

## File format API

```{r file_api, echo=FALSE,warning=FALSE,error=FALSE,output="asis"}
for (file_name in file_info$name) {
  arg_info <- file_info %>% filter(name == file_name)
  sub_out <- file_slot %>% 
    filter(file_name == !!file_name) %>% 
    select(struct, name, type, description)

  used_in <- comp_file %>%
    filter(file_name == !!file_name) %>%
    left_join(comp_info %>% select(comp_name = name, comp_label = label), by = "comp_name") %>%
    mutate(str = paste0("* [", comp_label, "](#", comp_label, "): ", arg_name, " (as ", direction, ")")) %>%
    pull(str)

  example <- sub_out %>%
    group_by(struct) %>%
    summarise(
      str = paste0(unique(struct), ": ", paste0("'", name, "'", collapse = ", "))
    ) %>%
    arrange(match(struct, c("obs", "var", "uns", "obsm", "obsp", "varm", "varp", "layers")))

  example_str <- c("    AnnData object", paste0("     ", example$str))
  
  out_str <- strip_margin(glue::glue("
    §### `{str_to_title(arg_info$label)}`
    §
    §{arg_info$description}
    §
    §Used in:
    §
    §{paste(used_in, collapse = '\n')}
    §
    §Slots:
    §
    §{paste(knitr::kable(sub_out, format = 'pipe'), collapse = '\n')}
    §
    §Example:
    §
    §{paste(example_str, collapse = '\n')}
    §
    §"), symbol = "§")
  cat(out_str)
}
```



## Component API

```{r comp_api, echo=FALSE,warning=FALSE,error=FALSE,output="asis"}
# todo: add description
# todo: add required info fields
for (comp_name in comp_info$name) {
  comp <- comp_info %>% filter(name == comp_name)
  sub_out <- comp_file %>% 
    filter(comp_name == !!comp_name) %>%
    left_join(file_info %>% select(file_name = name, file_desc = description, file_sdesc = short_description, file_label = label), by = "file_name") %>%
    transmute(
      Name = paste0("`--", arg_name, "`"),
      `File format` = paste0("[", str_to_title(file_label), "](#", file_label, ")"),
      Direction = direction,
      Description = file_sdesc
    )
  
  out_str <- strip_margin(glue::glue("
    §### `{str_to_title(comp$label)}`
    §
    §{ifelse(\"description\" %in% names(comp), comp$description, \"\")}
    §
    §Arguments:
    §
    §{paste(knitr::kable(sub_out, format = 'pipe'), collapse = '\n')}
    §"), symbol = "§")
  cat(out_str)
}
```